\section{Standard Symbols}
\label{sec:standard-symbols}

This section is the notation contract for the document.  The symbol table below
declares the reusable objects, but the rules in this opening subsection explain
how to read indexed expressions before looking up each individual symbol.

\subsection{Reading Conventions}
\label{subsec:notation-reading-conventions}

Every reusable symbol in this draft should have a declared domain, shape, or
local definition before it is used.  A symbol that appears across more than one
subsection belongs in the table below.  A temporary symbol used only inside one
display or one paragraph may be defined locally, but it should not silently
change the meaning of a tabled symbol.

\begin{enumerate}
  \item \textbf{Visual role is not the whole type.}
  The macros $\vect{\cdot}$, $\mat{\cdot}$, and $\tensor{\cdot}$ are visual
  reminders:
  \[
    \vect{a}\quad\text{vector-like},\qquad
    \mat{A}\quad\text{matrix-like},\qquad
    \tensor{x}\quad\text{tensor or tensor-family-like}.
  \]
  The actual rank and shape are determined by the displayed domain, not by the
  letter case alone.  For example, $\tensor{x}$ is rank four in a batch, while
  $\tensor{x}_{u\,v}^{c\,i}$ is a feature vector slice.

  \item \textbf{Declare dimensionality with membership.}
  Whenever a new variable is introduced with a domain, shape, or output space,
  declare it with $\in$:
  \[
    \tensor{x}\in\R^{B\times C\times H_x\times D_x},
    \qquad
    \widehat{r}_e\in\R,
    \qquad
    \mathcal{O}:\mathcal{P}(\R^{d_{\mathcal{O}}})\rightarrow\mathcal{Y}.
  \]
  Equality signs are reserved for definitions, identities, or assignments after
  the dimensional role has been made clear.

  \item \textbf{Sets, collections, and maps.}
  Calligraphic symbols denote sets or structured collections, such as
  $\mathcal{V}$, $\mathcal{E}$, $\mathcal{P}(\R^d)$, or an augmentation family
  $\mathcal{A}$.  Named maps such as $\Phi$, ${}_{\zeta}P$, and
  $\mathcal{O}$ are written as functions with explicit input and output spaces
  whenever their type matters.

  \item \textbf{The active graph convention.}
  The active market graph is
  \[
    \mathcal{G}=(\mathcal{V},\mathcal{E}),
    \qquad
    \mathcal{E}
    \subseteq
    \{(u,v)\in\mathcal{V}\times\mathcal{V}:u\ne v\}.
  \]
  An edge is written $e=(u,v)$, where $u$ is the base node and $v$ is the quote
  node.  The lower label $u\,v$ in an expression such as
  $\tensor{x}_{u\,v}$ is an ordered edge label, not multiplication.

  \item \textbf{Batch, channel, time, feature, and mixture order.}
  For exposed data and target tensors, the standard coordinate order is
  \[
    (b,c,i,d)
    =
    (\text{batch},\text{channel},\text{sequence or horizon},\text{feature}).
  \]
  Thus
  \[
    x^{b\,c\,i\,d}
    \quad\text{and}\quad
    f^{b\,c\,i\,d}
  \]
  are scalar feature coordinates.  For MDN component tensors, the standard
  coordinate order is
  \[
    (b,c,i,k,d)
    =
    (\text{batch},\text{channel},\text{horizon},\text{mixture component},
    \text{feature}).
  \]
  Thus $\mu^{b\,c\,i\,k\,d}$ and $\sigma^{b\,c\,i\,k\,d}$ are scalar
  coordinates of component $k$ at one batch, channel, and horizon.

  \item \textbf{The index $i$ is context-dependent.}
  The same letter $i$ is used for input positions and forecast positions.  The
  object determines the active range:
  \[
    i=1,\ldots,H_x
    \quad\text{for input windows},\qquad
    i=1,\ldots,H_f
    \quad\text{for future windows}.
  \]
  When the distinction must be emphasized in prose, we say input position for
  $H_x$ and forecast step or horizon for $H_f$.

  \item \textbf{Channel time is channel-relative.}
  A channel $c$ represents a native time scale, such as \field{1m},
  \field{1h}, or \field{1d}.  The same forecast index $i$ can therefore mean
  different physical elapsed time on different channels.  When elapsed duration
  is needed, write it as $i\Delta_c$, where $\Delta_c$ is the native step
  duration of channel $c$.

  \item \textbf{External time is not a tensor axis unless declared.}
  The symbol $t$ denotes an anchor time or repeated evaluation time.  It is
  written as an argument, as in $\tensor{x}_{u\,v}(t)$ or
  ${}_{\psi}\mathfrak{D}_{u\,v}^{c\,i}(t)$, rather than as one of the core
  tensor axes.  The tensor axes describe one sampled window around that anchor.

  \item \textbf{Sample-level and batch-level notation.}
  A sample-level edge object keeps its edge label visible:
  \[
    \tensor{x}_{u\,v}(t)\in\R^{C\times H_x\times D_x}.
  \]
  A batch-level object may suppress the edge labels and use the leading batch
  index:
  \[
    \tensor{x}(t)\in\R^{B\times C\times H_x\times D_x}.
  \]
  Logically, each batch sample still carries an edge identity
  $e^b=(u^b,v^b)\in\mathcal{E}$.  When batches are homogeneous, all samples may
  share the same edge.  When batches mix edges, the implementation must route
  each sample by its edge label or use an explicitly edge-conditioned model.

  \item \textbf{Lower-right labels and lower-left namespaces.}
  Lower-right subscripts usually label semantic objects, such as edges,
  endpoints, or named coordinates:
  \[
    \tensor{x}_{u\,v},\qquad
    \widehat{r}_{e},\qquad
    \mat{C}_{y}.
  \]
  Lower-left tags mark a family or parameter namespace, not an extra tensor
  coordinate:
  \[
    {}_{x}\tensor{m}
    \quad\text{input-mask family},\qquad
    {}_{f}\tensor{m}
    \quad\text{future-mask family},\qquad
    {}_{\psi}p
    \quad\text{density emitted by the MDN family}.
  \]
  The lower-left tags $\Phi$, $\zeta$, and $\psi$ are used to keep the
  representation encoder, VICReg projector, and MDN forecast head visually
  separated.

  \item \textbf{Parenthesized labels are semantic labels, not powers.}
  Parentheses in indices denote labels such as augmented views, residual blocks,
  or selected semantic coordinates:
  \[
    (1),(2) \quad\text{augmented views},\qquad
    (\{1,2\}) \quad\text{paired augmented-view object},\qquad
    (r) \quad\text{selected scalar return coordinate}.
  \]
  Thus $f^{c\,i}_{(r)}$ means the scalar return coordinate of the future vector;

  \item \textbf{Source coordinates and target coordinates.}
  %NOTE: #TODO not finish, this part i dont know if its clear.
  The input source registry has $D_x$ normalized kline coordinates.  The future
  target tensor has $D_f$ coordinates selected by the ordered list
  $\mathcal{J}_f$.  A target coordinate index $d=1,\ldots,D_f$ is therefore a
  slot inside the selected target vector, while a source coordinate such as
  $d_{(r)}=4$ refers to the original normalized kline registry.  When the scalar
  return readout is used, the source coordinate $d_{(r)}$ must appear in
  $\mathcal{J}_f$, and the label $(r)$ denotes its corresponding target slot.

  \item \textbf{Masks are evidence selectors.}
  Mask values live in $\{0,1\}$.  The input mask ${}_{x}\tensor{m}$ says which
  past channel-time slices are usable by the encoder.  The future mask
  ${}_{f}\tensor{m}$ says which future channel-horizon slices are valid
  supervised evidence for the MDN loss.  A masked-out slice is not an observed
  zero-valued market event.

  \item \textbf{Distributions and densities are different objects.}
  Predictive distributions are written with fraktur symbols, for example
  \[
    {}_{\psi}\mathfrak{D}_{u\,v}^{c\,i}
    \in
    \mathcal{P}(\R^{D_f}).
  \]
  Their densities are written with $p$, for example
  \[
    {}_{\psi}p_{u\,v}^{c\,i}
    (\cdot\given\tensor{z}_{u\,v})
    :
    \R^{D_f}
    \rightarrow
    \Rnonneg.
  \]
  The distribution is the probabilistic object.  The density is the function
  used to evaluate likelihoods and training scores.

  \item \textbf{Observers read distributions.}
  Observer operators do not replace the predictive distribution field.  They
  read it:
  \[
    \mathcal{O}
    :
    \mathcal{P}(\R^{d_{\mathcal{O}}})
    \rightarrow
    \mathcal{Y}.
  \]
  Hatted quantities such as $\widehat{\tensor{f}}$, $\widehat{r}_{e}^{c\,i}$,
  and $\widehat{\vect{y}}$ are observer outputs or recovered estimates.  They
  should not be confused with the full uncertainty-bearing distribution.

  \item \textbf{Suppressed indices must be fixed by context.}
  Later sections sometimes suppress indices to keep equations readable.  For
  example, Section~\ref{sec:edges-to-nodes} writes $\widehat{r}_e$ and
  $\gamma_e$ after fixing a channel, forecast step, scalar observer, and usable
  edge set.  Suppression is allowed only when the surrounding text states which
  indices have been fixed.

  \item \textbf{Code field names are written as fields, not symbols.}
  Implementation names such as \field{features}, \field{future\_features},
  \field{mask}, \field{future\_mask}, \field{edge\_id}, \field{log\_pi},
  \field{mu}, and \field{sigma} are written with \verb|\field{...}|.  When a
  code field corresponds to a mathematical object, the source-code interface
  appendix states the equivalence.
\end{enumerate}

\calloutbox{Notation Contract.}{\\%
  The notation should make hidden implementation assumptions visible.  When a
  tensor changes axis order, when a batch begins mixing edges, when a target
  registry changes, or when a readout becomes part of a training objective, this
  section and the source-code interface contract should be updated together.
}

\subsection{Symbol Table}
\label{subsec:symbol-table}

\begin{center}
\rowcolors{2}{SymbolRow}{white}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.10\textwidth}
                  >{\raggedright\arraybackslash}p{0.28\textwidth}
                  >{\raggedright\arraybackslash}p{0.50\textwidth}}
\toprule
Symbol & Domain or shape & Meaning \\
\midrule
$\R$ & $\R$ & Real numbers. \\
$\N$ & $\N = \{1,2,3,\ldots\}$ & Positive integers. \\
$\N_{\ge 0}$ & $\N_{\ge 0} = \{0,1,2,\ldots\}$ & Nonnegative integers. \\
$\Rpos$ & $\Rpos = \{x \in \R : x > 0\}$ & Positive real numbers. \\
$\Rnonneg$ & $\Rnonneg = \{x \in \R : x \ge 0\}$ & Nonnegative real numbers. \\
\midrule
$\mathcal{G}$ & $\mathcal{G}=(\mathcal{V},\mathcal{E})$ & Active directed graph. \\
$\mathcal{V}$ & finite, $|\mathcal{V}|=N$ & Node set. \\
$\mathcal{E}$ & $\mathcal{E}\subseteq\{(u,v)\in\mathcal{V}\times\mathcal{V}:u\ne v\}$ & Active directed edge set of staged traded instruments. \\
$\mathcal{E}_{\mathrm{use}}$ & $\mathcal{E}_{\mathrm{use}}\subseteq\mathcal{E}$ & Usable edge subset selected for one graph recovery solve after masks and observer choices are applied. \\
\midrule
$B$ & $B \in \N$ & Batch size. \\
$C$ & $C \in \N$ & Active channel count. \\
$H_x$ & $H_x \in \N$ & Input sequence length. \\
$H_f$ & $H_f \in \N$ & Forecast sequence length. \\
$D_x$ & $D_x \in \N$ & Input features count. \\
$D_f$ & $D_f \in \N$ & Forecast feature count. \\
$D_e$ & $D_e \in \N$ & Encoding or embedding dimension. \\
$D_p$ & $D_p \in \N$ & VICReg projector width. \\
$S$ & $S\in\N$ & Number of sampled scenario trajectories. \\
$H_x'$ & $H_x' \in \N$ & Optional internal encoder sequence length. \\
$H_{\Phi}$ & $H_{\Phi} \in \N$ & Hidden width in the representation encoder. \\
$H_{\psi}$ & $H_{\psi} \in \N$ & Hidden width in the MDN backbone. \\
$R_{\psi}$ & $R_{\psi} \in \N_{\ge 0}$ & Number of residual blocks in the MDN backbone. \\
$K$ & $K \in \N$ & Number of density-mixture components. \\
$N$ & $N = |\mathcal{V}| \in \N$ & Active node count. \\
$L$ & $L=|\mathcal{E}|\le N(N-1)$ & Active edge count. \\
\midrule
$b$ & $b \in \{1,\ldots,B\}$ & Batch sample index. \\
$c$ & $c \in \{1,\ldots,C\}$ & Channel index. \\
$i$ & $i \in \{1,\ldots,H_x\}$ or $i \in \{1,\ldots,H_f\}$ & Sequence index; the active range is determined by whether the tensor uses the input axis $H_x$ or the forecast axis $H_f$. \\
$d$ & $d \in \{1,\ldots,D_x\}$, $d \in \{1,\ldots,D_f\}$, or $d \in \{1,\ldots,D_p\}$ & Feature-coordinate or projector-coordinate index; the active range is determined by whether the tensor uses the input-feature axis $D_x$, the future-feature axis $D_f$, or the projector axis $D_p$. \\
$k$ & $k \in \{1,\ldots,K\}$ & Mixture-component index. \\
$r$ & $r \in \{1,\ldots,R_{\psi}\}$ & Residual-block index in the MDN backbone. \\
$t$ & $t \in \mathcal{T}$ & Optional evaluation-time index. \\
$\Delta_c$ & positive time duration & Native step duration of channel $c$; forecast step $i$ corresponds to elapsed duration $i\Delta_c$. \\
$u$ & $u \in \mathcal{V}$ & Base node. \\
$v$ & $v \in \mathcal{V}$ & Quote node. \\
$e$ & $e \in \mathcal{E}$ & Graph edge. \\
$e^b$ & $e^b=(u^b,v^b)\in\mathcal{E}$ & Directed edge label carried by batch sample $b$. \\
$g$ & $g \in \mathcal{V}$ & Gauge or reference node used to remove the additive ambiguity in node recovery. \\
\midrule
$\mathcal{T}$ & $\mathcal{T}$ ordered set & Evaluation-time index set when repeated model evaluations are discussed. \\
$m$ & $m \in \N$ & Generic observer output or covariance coordinate count. \\
$d_{\mathcal{O}}$ & $d_{\mathcal{O}} \in \{1,D_f\}$ & Observer input dimension: scalar distribution or full future-vector distribution. \\
\midrule
$\tensor{x}_{u\,v}(t)$ & $\tensor{x}_{u\,v}(t) \in \R^{C \times H_x \times D_x}$, $(u,v) \in \mathcal{E}$ & Normalized kline input window carried by the directed edge from $u$ to $v$ at time $t$. \\
$\tensor{x}_{u\,v}^{b}(t)$ & $\tensor{x}_{u\,v}^{b}(t) \in \R^{C \times H_x \times D_x}$ & Normalized input window for sample $b$, carried by edge $e=(u,v)$. \\
$\tensor{x}_{u\,v}^{b\,c\,i}$ & $\tensor{x}_{u\,v}^{b\,c\,i} \in \R^{D_x}$ & Normalized kline feature slice for one sample, edge, channel, and input position. \\
$x_{u\,v}^{b\,c\,i\,d}$ & $x_{u\,v}^{b\,c\,i\,d} \in \R$ & Scalar coordinate $d$ of the normalized slice $\tensor{x}_{u\,v}^{b\,c\,i}$. \\
$\tensor{x}$ & $\tensor{x} \in \R^{B \times C \times H_x \times D_x}$ & Batch formed by stacking edge-labeled input windows $\tensor{x}_{u\,v}^{b}$. \\
${}_{x}\tensor{m}_{u\,v}$ & ${}_{x}\tensor{m}_{u\,v} \in \{0,1\}^{C \times H_x}$ & Input validity mask for edge $e=(u,v)$. \\
$\tensor{m}_x^{b}$ & $\tensor{m}_x^{b} \in \{0,1\}^{C \times H_x}$ & Input validity mask for sample $b$. \\
$\tensor{m}_x$ & $\tensor{m}_x \in \{0,1\}^{B \times C \times H_x}$ & Batch input validity mask. \\
$m_x^{b\,c\,i}$ & $m_x^{b\,c\,i} \in \{0,1\}$ & Input-mask slice for one sample, channel, and input position. \\
${}_{f}\tensor{m}_{u\,v}$ & ${}_{f}\tensor{m}_{u\,v} \in \{0,1\}^{C \times H_f}$ & Future validity mask for edge $e=(u,v)$. \\
$\tensor{m}_f$ & $\tensor{m}_f \in \{0,1\}^{B \times C \times H_f}$ & Future validity mask. \\
$m_f^{b\,c\,i}$ & $m_f^{b\,c\,i} \in \{0,1\}$ & Future-mask slice for one sample, channel, and horizon. \\
$\tensor{f}$ & $\tensor{f} \in \R^{B \times C \times H_f \times D_f}$ & Future target batch. \\
$\vect{f}$ & $\vect{f} \in \R^{D_f}$ & Generic future target vector. \\
$\tensor{f}^{b\,c\,i}$ & $\tensor{f}^{b\,c\,i} \in \R^{D_f}$ & Future target slice for one sample, channel, and horizon. \\
$f^{b\,c\,i\,d}$ & $f^{b\,c\,i\,d} \in \R$ & Scalar target coordinate $d$ of the future slice $\tensor{f}^{b\,c\,i}$. \\
$\mathcal{J}_f$ & $\mathcal{J}_f=(d_1,\ldots,d_{D_f})$, $d_a\in\{1,\ldots,D_x\}$ & Ordered source-coordinate list used to form the future target tensor. \\
\midrule
$\Phi,\zeta,\psi$ & learned parameter collections & Representation-map, VICReg-projector, and forecast-head parameters. \\
$\Phi$ & $\Phi:\R^{C \times H_x \times D_x}\times\{0,1\}^{C \times H_x}\rightarrow\R^{H_x' \times D_e}$ & Sequence encoder map for one sample. \\
$\tensor{z}_{u\,v}$ & $\tensor{z}_{u\,v}\in\R^{D_e}$ & Reduced edge representation for directed edge $e=(u,v)$. \\
$\tensor{z}$ & $\tensor{z} \in \R^{B \times D_e}$ & Representation batch. \\
\midrule
$\tilde{\alpha}_{u\,v}^{c\,i\,k}$ & $\tilde{\alpha}_{u\,v}^{c\,i\,k} \in \R$ & Raw mixture activation before normalization. \\
$\vect{\tilde{\alpha}}_{u\,v}^{c\,i}$ & $\vect{\tilde{\alpha}}_{u\,v}^{c\,i}\in\R^K$ & Raw mixture-activation vector for one edge, channel, and horizon. \\
$\tensor{\tilde{\alpha}}$ & $\tensor{\tilde{\alpha}} \in \R^{B \times C \times H_f \times K}$ & Batch raw mixture activations. \\
$\alpha_{u\,v}^{c\,i\,k}$ & $\alpha_{u\,v}^{c\,i\,k}\in[0,1]$ & Bishop-style mixture coefficient for component $k$, with $\sum_k \alpha_{u\,v}^{c\,i\,k}=1$. \\
$\vect{\alpha}_{u\,v}^{c\,i}$ & $\vect{\alpha}_{u\,v}^{c\,i} \in [0,1]^K$ & Mixture-coefficient vector for one edge, channel, and horizon. \\
$\tensor{\mu}$ & $\tensor{\mu} \in \R^{B \times C \times H_f \times K \times D_f}$ & Batch component means. \\
$\vect{\mu}_{u\,v}^{c\,i\,k}$ & $\vect{\mu}_{u\,v}^{c\,i\,k} \in \R^{D_f}$ & Mean vector of one Gaussian component for edge $e=(u,v)$. \\
$\vect{\beta}_{u\,v}^{c\,i\,k}$ & $\vect{\beta}_{u\,v}^{c\,i\,k} \in \R^{D_f}$ & Raw scale vector emitted by the MDN head before the positive transform. \\
$\tensor{\beta}$ & $\tensor{\beta} \in \R^{B \times C \times H_f \times K \times D_f}$ & Batch raw scale vectors emitted before the positive transform. \\
$\tensor{\sigma}$ & $\tensor{\sigma} \in \Rpos^{B \times C \times H_f \times K \times D_f}$ & Batch positive component scales. \\
$\vect{\sigma}_{u\,v}^{c\,i\,k}$ & $\vect{\sigma}_{u\,v}^{c\,i\,k} \in \Rpos^{D_f}$ & Positive component scale vector. \\
$\bar{\sigma}^{b\,c\,i\,k\,d}$ & $\bar{\sigma}^{b\,c\,i\,k\,d}\in\Rpos$ & Protected scale coordinate used inside the MDN training loss after optional lower or upper clamping. \\
$\sigma_{\min},\sigma_{\max}$ & $\sigma_{\min}\in\Rpos$, optional $\sigma_{\max}\in\Rpos$ & Optional lower and upper numerical scale clamps for MDN training. \\
$\eps$ & $\eps \in \Rpos$ & Positive numerical floor. \\
$\mat{\Sigma}_{u\,v}^{c\,i\,k}$ & $\mat{\Sigma}_{u\,v}^{c\,i\,k} \in \R^{D_f \times D_f}$ & Diagonal covariance of one component. \\
$\softmax$ & $\softmax:\R^K\rightarrow[0,1]^K$ & Mixture-coefficient normalization operator. \\
$\softplus$ & $\softplus:\R^{D_f}\rightarrow\Rpos^{D_f}$ & Positive scale transform applied coordinatewise. \\
$\diag$ & $\diag:\R^{D_f}\rightarrow\R^{D_f \times D_f}$ & Diagonal-matrix constructor. \\
$\mathcal{N}(\vect{f};\vect{\mu},\mat{\Sigma})$ & $\mathcal{N}:\R^{D_f}\rightarrow\Rnonneg$ & Gaussian density with mean $\vect{\mu}$ and covariance $\mat{\Sigma}$. \\
${}_{\psi}p_{u\,v}^{c\,i}$ & ${}_{\psi}p_{u\,v}^{c\,i}(\cdot \given \tensor{z}_{u\,v}):\R^{D_f}\rightarrow\Rnonneg$ & Conditional predictive density for edge $e=(u,v)$, channel, and horizon. \\
${}_{\psi}p_{(r),u\,v}^{c\,i}$ & ${}_{\psi}p_{(r),u\,v}^{c\,i}(\cdot \given \tensor{z}_{u\,v}):\R\rightarrow\Rnonneg$ & Scalar edge-return predictive density for edge $e=(u,v)$, channel, and horizon. \\
$d_{(r)}$ & $d_{(r)}\in\{1,\ldots,D_x\}$ & Source-registry coordinate selected as the scalar edge return; for close return in the normalized kline registry, $d_{(r)}=4$. \\
$(r)$ & selected target-slot label in $\{1,\ldots,D_f\}$ & Semantic label for the scalar return coordinate inside the future target vector. \\
${}_{d}\lambda^{(d)}$ & ${}_{d}\lambda^{(d)}\in\Rnonneg$ & Optional feature-coordinate weight in the MDN likelihood. \\
${}_{c}\lambda^{(c)}$ & ${}_{c}\lambda^{(c)}\in\Rnonneg$ & Optional channel weight in the MDN loss. \\
${}_{i}\lambda^{(i)}$ & ${}_{i}\lambda^{(i)}\in\Rnonneg$ & Optional horizon weight in the MDN loss. \\
${}_{f}\omega_{u\,v}^{b\,c\,i}$ & ${}_{f}\omega_{u\,v}^{b\,c\,i}\in\Rnonneg$ & Nonnegative MDN training weight for edge $e=(u,v)$, combining the future mask with optional channel and horizon weights. \\
\midrule
$\mathcal{P}(\R^d)$ & $\mathcal{P}(\R^d)$ & Probability distributions on $\R^d$. \\
${}_{\psi}\mathfrak{D}_{u\,v}^{c\,i}$ & ${}_{\psi}\mathfrak{D}_{u\,v}^{c\,i} \in \mathcal{P}(\R^{D_f})$ & Predictive distribution for one future target vector on edge $e=(u,v)$. \\
${}_{\psi}\mathfrak{D}_{(r),u\,v}^{c\,i}$ & ${}_{\psi}\mathfrak{D}_{(r),u\,v}^{c\,i} \in \mathcal{P}(\R)$ & Scalar edge-return predictive distribution for edge $e=(u,v)$. \\
$\mathfrak{D}$ & $\mathfrak{D} \in \mathcal{P}(\R^{D_f})$ & Generic predictive distribution used in observer definitions. \\
$\widehat{\tensor{f}}$ & $\widehat{\tensor{f}} \in \R^{B \times C \times H_f \times D_f}$ & Batch expectation of future target vectors. \\
$\widehat{\tensor{f}}_{u\,v}^{c\,i}$ & $\widehat{\tensor{f}}_{u\,v}^{c\,i} \in \R^{D_f}$ & Expected future target slice for edge $e=(u,v)$. \\
$r_{u\,v}^{c\,i}$ & $r_{u\,v}^{c\,i} \in \R$ & Scalar return value for edge $e=(u,v)$, channel, and horizon. \\
$R_e^{c\,i}$ & $R_e^{c\,i}\in\R$ & Cumulative scalar edge return from the anchor to forecast step $i$. \\
\midrule
$\mathcal{O}$ & $\mathcal{O}:\mathcal{P}(\R^{d_{\mathcal{O}}})\rightarrow\mathcal{Y}$ & Observer operator for scalar or vector predictive distributions. \\
$\mathcal{O}_{\E}$, $\mathcal{O}_{\Var}$, $\mathcal{O}_{\Quant\,\tau}$, $\mathcal{O}_{\ES\,\tau}$, $\mathcal{O}_{\Risk}$ & $\mathcal{O}_{\cdot}:\mathcal{P}(\R^{d_{\mathcal{O}}})\rightarrow\mathcal{Y}$ & Named observer examples. \\
$\E$, $\Var$, $\Cov$, $\Quant$, $\ES$ & Operators on random variables or probability distributions & Expectation, variance, covariance, quantile, and expected shortfall. \\
$\mathcal{Y}$ & $\mathcal{Y}$ set & Observer output space. \\
$\tau$ & $\tau \in (0,1)$ & Quantile or expected-shortfall level. \\
$\widehat{r}_{e}^{c\,i}$ & $\widehat{r}_{e}^{c\,i} \in \R$ & Scalar edge-return value read by an observer. \\
$\widehat{R}_{e}^{c\,i}$ & $\widehat{R}_{e}^{c\,i}\in\R$ & Expected cumulative scalar edge return from the anchor to forecast step $i$. \\
$\vect{F}_{e}^{c,1:H_f}$ & $\vect{F}_{e}^{c,1:H_f}\in(\R^{D_f})^{H_f}$ & Forecast trajectory for edge $e$ and channel $c$. \\
$s_{e}^{c\,i\,k}$ & $s_{e}^{c\,i\,k}\in\R$ & Component-mode score for component $k$ at edge $e$, channel $c$, and horizon $i$. \\
$\widehat{\kappa}_{e}^{c}$ & $\widehat{\kappa}_{e}^{c}\in\{1,\ldots,K\}^{H_f}$ & Discrete component-path index sequence selected by the component-path trajectory readout. \\
$\widehat{\vect{F}}_{e,\mathrm{dens}}^{c,1:H_f}$ & $\widehat{\vect{F}}_{e,\mathrm{dens}}^{c,1:H_f}\in(\R^{D_f})^{H_f}$ & Maximum-density predictive trajectory readout. \\
$\widehat{\vect{F}}_{e,\mathrm{comp}}^{c,1:H_f}$ & $\widehat{\vect{F}}_{e,\mathrm{comp}}^{c,1:H_f}\in(\R^{D_f})^{H_f}$ & Component-path representative trajectory readout. \\
$\mathcal{R}_{\mathrm{path}}$ & $\mathcal{R}_{\mathrm{path}}:(\R^{D_f})^{H_f}\rightarrow\Rnonneg$ & Optional trajectory regularizer used by maximum-density path readouts. \\
$\lambda_{\Delta}$ & $\lambda_{\Delta}\in\Rnonneg$ & Smoothness or jump-penalty weight for component-path readouts. \\
$\gamma_{e}^{c\,i}$ & $\gamma_{e}^{c\,i} \in \Rpos$ & Scalar confidence or precision weight. \\
$\widehat{r}_e$ & $\widehat{r}_e \in \R$ & Edge-return observation for a fixed channel and forecast step. \\
$\gamma_e$ & $\gamma_e \in \Rpos$ & Edge confidence or precision weight for a fixed channel and forecast step. \\
$\delta$ & $\delta \in \Rpos$ & Positive variance-stabilizing floor. \\
\midrule
$R_i$ & $R_i \in \R$ & Scalar return coordinate in a second-order observer. \\
$\Sigma$ & $\Sigma \in \R^{m \times m}$ & Covariance matrix for $m$ scalar return coordinates. \\
$\rho$ & $\rho \in \R^{m \times m}$ & Correlation matrix derived from $\Sigma$. \\
\midrule
$\eta_u(t)$ & $\eta_u(t) \in \Rpos$ & Positive node valuation at node $u$ and time $t$; the time argument may be omitted when fixed. \\
$\xi_u(t)$ & $\xi_u(t) \in \R$ & Log node valuation, $\xi_u(t)=\log \eta_u(t)$; the time argument may be omitted when fixed. \\
$h_u(t)$ & $h_u(t)\in\R$ & Signed portfolio holding coordinate at node $u$ and time $t$.  Positive values denote long or positive exposure, negative values denote short, borrowed, or liability exposure, and zero denotes no active holding. \\
$\vect{h}(t)$ & $\vect{h}(t)=(h_u(t))_{u\in\mathcal{V}}\in\R^N$ & Node-level portfolio holding state. \\
$q_e$ & $q_e \in \Rpos$ & Observed edge price. \\
$\ell_e$ & $\ell_e \in \R$ & Log edge price, $\ell_e=\log q_e$. \\
$r_e$ & $r_e \in \R$ & Signed scalar edge return. \\
$y_u$ & $y_u \in \R$ & Scalar node return or node potential coordinate. \\
$\vect{y}$ & $\vect{y} \in \R^N$ & Node-return or node-potential vector. \\
$\vect{\widehat{r}}$ & $\vect{\widehat{r}} \in \R^L$ & Vector of observed or predicted edge returns. \\
$\vect{\eps}_r$ & $\vect{\eps}_r\in\R^L$ & Edge-recovery residual, $\vect{\widehat{r}}-\mat{A}\widehat{\vect{y}}$. \\
$\mathcal{Q}_r$ & $\mathcal{Q}_r\in\Rnonneg$ & Weighted residual diagnostic for node recovery. \\
$\mat{A}$ & $\mat{A} \in \R^{L \times N}$ & Directed edge-node incidence matrix. \\
$\mat{A}_g$ & gauge-fixed incidence matrix & Incidence matrix after removing the gauge coordinate or otherwise restricting to free node coordinates. \\
$\mat{\Gamma}$ & $\mat{\Gamma} \in \R^{L \times L}$ & Diagonal edge-confidence matrix. \\
$\mat{L}_{\gamma}$ & $\mat{L}_{\gamma} \in \R^{N \times N}$ & Confidence-weighted graph Laplacian, $\mat{A}^{\top}\mat{\Gamma}\mat{A}$. \\
$\mat{C}_r$ & $\mat{C}_r \in \R^{L \times L}$ & Edge-return covariance matrix. \\
$\mat{C}_y$ & $\mat{C}_y \in \R^{N \times N}$ & Recovered node covariance matrix, understood after gauge fixing or on the quotient space. \\
$\mat{C}_y^{(g)}$ & gauge-fixed node covariance & Recovered node covariance in the free coordinates after the gauge node has been removed. \\
$\mat{V}$ & $\mat{V} \in \R^{(N-1) \times (N-1)}$ & Eigenvector matrix for gauge-fixed node covariance modes. \\
$\Lambda$ & $\Lambda \in \R^{(N-1) \times (N-1)}$ & Diagonal eigenvalue matrix for gauge-fixed node covariance modes. \\
$d(\vect{y},\vect{y}')$ & $d:\R^N\times\R^N\rightarrow\Rnonneg$ & Mahalanobis distance between node states. \\
\bottomrule
\end{longtable}
\end{center}
