\newpage{}
\section[Market Graph Model]{Market Graph Model $(\mathcal{V},\mathcal{E})$}
\label{sec:edges-and-nodes}

In \Cuwacunu{}%
\note{
  www.waajacu.com/
}, we model%
\note{
  The market graph is the mathematical object shared by the representation,
  edge forecasting, risk \& value at node observers after the node-recovery section.  It
  treats assets as nodes, traded instruments prices as directed edge relations.
}
the active market universe%
\note{
  The active universe is a subset of all the assets in the market,
  traded instrument, and the historic source records attached to the 
  edge.  It may be smaller than the exchange's full listed universe.
} 
as a directed graph%
\note{
  The direction follows the base-to-quote convention for traded symbols.
  Reversing the order is assumed to be the inverse quotation price, and changes the
  economic meaning of the edge.
}. 
\[
  \mathcal{G}=(\mathcal{V},\mathcal{E}).
\]
Nodes $\mathcal{V}$ are market assets, and the directed edges $\mathcal{E}$
are traded instrument symbols%
\note{
  An edge $e=(u,v)\in\mathcal{E}$ is read from base node $u$ to quote node $v$.
  For example, \field{BTCUSDT} determines
  $e=(\texttt{BTC},\texttt{USDT})$, with \texttt{BTC} as base node and
  \texttt{USDT} as quote node.
  The asset at the nodes could be:
  $
    \{\text{\field{ADA}}, \text{\field{BNB}}, \text{\field{BTC}},
    \text{\field{DOGE}}, \text{\field{ETH}}, \text{\field{FDUSD}},
    \text{\field{LTC}}, \text{\field{SOL}}, \text{\field{USDT}},
    \text{\field{XRP}},\ldots\}
    \subseteq \mathcal{V}
  $
  and the staged traded instrument symbols at the edges are like
  $
    \{\text{\field{ADAUSDT}}, \text{\field{BNBBTC}},
    \text{\field{BTCETH}}, \text{\field{DOGEUSDT}},
    \text{\field{XRPADA}},\ldots\}
    \subseteq \mathcal{E}
  $
}
. So that at time $t$%
\note{
  The index $t$ is the sampling anchor used by the model.  It is
  related to kline keys such as \field{close\_time}, but it should not be read as
  the raw \field{close\_time} of every channel position.  Multi-channel alignment
  is described in Appendix~\ref{app:sequence-synchronization}.
}
, the normalized data tensor%
\note{
  See section~\ref{subsec:input-data} for more details on the data.
}
held by the edge in between nodes $u,v\in\mathcal{V}$, is denoted as: 
\[
  e=(u,v)\in\mathcal{E}
  \quad
  \longmapsto
  \quad
  \tensor{x}_{u\,v}(t),
\]

The holdings of the portfolio are recorded on nodes%
\note{
  We use index $u$ in the holding's $h_u(t)$ because on edge $e=(u,v)$, 
  it is the base endpoint of that edge that we are referencing.
}:
\[
  u \in \mathcal{V}
  \quad
  \longmapsto
  \quad
  h_u(t).
\]
  
\calloutbox{Edge-Data \& Node-State Disambiguation.}{\\%
  Asset holdings at the base node $h_{u}$
  have a price readout $\tensor{x}_{u\,v}(t)$ of $u$ in terms of $v$,
  thus prices are quotations, not states stored inside either node.  Section~\ref{sec:edges-to-nodes}
  describes how node valuations are recovered from edge readouts.
}

There are $N$ nodes and $L=|\mathcal{E}|$ active directed edges, with
$L\le N(N-1)$%
\note{
  The complete directed graph without self-edges would contain $N(N-1)$
  directed edges.  The active graph need not contain all of them; it contains
  the staged traded instrument relations available to the model.  Both
  directions are distinct when both are present, so $(u,v)$ and $(v,u)$ are
  different directed quotations.  A self-quotation such as \field{BTCBTC} is
  not considered valid.
}.

We will later present observer operators to read standard quantities such as
risk, exposure, entropy, and others. 
