\newpage{}
\section{Edge Value Forecasting}
\label{sec:edge-forecast-head}

We use mixture density networks in the sense of Bishop~\cite{bishop1994mdn},
to forecast the normalized \texttt{kline} future attached to each directed edge
$e=(u,v) \in \mathcal{E}$%
\note{
  In the current edge-specialized setting, one forecast head is trained for
  each directed edge $e=(u,v) \in \mathcal{E}$.  The notation below writes
  $\psi$ without adding an edge subscript; when needed, read it as the
  parameter collection belonging to the active edge.
}.
This means that instead of predicting only one value per feature, we
model a conditional probability density for each future feature vector
$\tensor{f}_{u\,v}^{c\,i}\in\R^{D_f}$.%
\note{
  This is
  important because the future market state may be multi-modal: several different
  future moves can be plausible under the same current representation.
}

The edge prediction head consumes the edge representation exported by Section~\ref{sec:representation}. 
\[
  \tensor{z}_{u\,v} \in \R^{D_e}.
\]

It then tries to estimate the future normalized \texttt{kline} window: 
\[
  \tensor{f}_{u\,v} \in \R^{C \times H_f \times D_f},
  \quad or \quad
  \tensor{f}_{u\,v}^{c\,i} \in \R^{D_f}.
\]

For this, the model creates%
\note{
  A mixture of $K$ Gaussian distributions creates $k = 1,\ldots,K$
  possible centers and spreads for that future, with mixture weights expressing
  how much probability each component carries.
  The density returns one scalar likelihood value for the whole future feature
  vector, not one forecast value per feature.  Feature-level predictions live in
  the component means and scales.  The diagonal covariance assumption factorizes
  each Gaussian component coordinatewise, but the mixture still represents a
  distribution over the full $D_f$-dimensional target vector.
}

\[
  \text{distribution}\quad
  {}_{\psi}\mathfrak{D}_{u\,v}^{c\,i}
  \quad\text{with density}\quad
  {}_{\psi}p_{u\,v}^{c\,i}(\cdot\given\tensor{z}_{u\,v}),
  \quad\text{parameterized by}\quad
  \left\{
    \alpha_{u\,v}^{c\,i\,k},
    \vect{\mu}_{u\,v}^{c\,i\,k},
    \mat{\Sigma}_{u\,v}^{c\,i\,k}
  \right\}_{k=1}^{K}.
\]


Here $\alpha$ is the component weight, $\vect{\mu}$ is the Gaussian mean, and
$\mat{\Sigma}$ is the component covariance matrix%
\note{
  The network does not emit every constrained parameter directly ($\alpha$, $\vect{\mu}$, $\mat{\Sigma}$).  
  It emits ($\tilde{\alpha}$,$\vect{\mu}$, $\vect{\beta}$), 
  raw mixture activations $\tilde{\alpha}$, component means $\vect{\mu}$, and raw
  scale vectors $\vect{\beta}$.  The raw activations are normalized into
  weights $\alpha$, and the raw scales are transformed into positive scales
  before forming the covariance matrices $\mat{\Sigma}$.
}.














\newpage{}
\subsection{Edge Forecast Mixture Density Network}
\label{subsec:mdn-forecast}

Let $H_{\psi}\in\N$ be the hidden width of the MDN backbone and let
$R_{\psi}\in\N_{\ge 0}$ be the number of residual Multi-Layer Perceptron blocks.
Each block uses two learned affine maps, layer normalization, and a Sigmoid
Linear Unit activation ($\operatorname{SiLU}$).
The first layer maps one edge representation to hidden space%
\note{
  $\operatorname{SiLU}$ is the coordinatewise Sigmoid Linear Unit activation,
  $\operatorname{SiLU}(x)=x/(1+\exp(-x))$. 
}:
\[
  {}_{\psi}\vect{h}^{(0)}
  =
  \operatorname{SiLU}
  \left(
    {}_{\psi}\mat{W}_{0}\cdot\tensor{z}_{u\,v}
    +
    {}_{\psi}\vect{b}_{0}
  \right)
  \in \R^{H_{\psi}}.
\]
Each residual block keeps the same width $H_{\psi}$.
A typical block has the form
\[
  {}_{\psi}\vect{q}^{(r)}
  =
  \operatorname{SiLU}
  \left(
    {}_{\psi}\mat{W}^{(r)}_{a_1}\cdot
    \operatorname{LayerNormalization}^{(r)}_{a_1}({}_{\psi}\vect{h}^{(r-1)})
    +
    {}_{\psi}\vect{b}^{(r)}_{a_1}
  \right)
  \in \R^{2H_{\psi}},
\]
\[
  {}_{\psi}\widetilde{\vect{h}}^{(r)}
  =
  {}_{\psi}\mat{W}^{(r)}_{a_2}\cdot{}_{\psi}\vect{q}^{(r)}
  +
  {}_{\psi}\vect{b}^{(r)}_{a_2}
  \in \R^{H_{\psi}},
\]
and
\[
  {}_{\psi}\vect{h}^{(r)}
  =
  \operatorname{SiLU}
  \left(
    \operatorname{LayerNormalization}^{(r)}_{a_2}
    \left(
      {}_{\psi}\vect{h}^{(r-1)}
      +
      {}_{\psi}\widetilde{\vect{h}}^{(r)}
    \right)
  \right)
  \in \R^{H_{\psi}}.
\]
After the residual stack, the backbone applies layer normalization ($\operatorname{LayerNormalization}$)%
\note{
  $\operatorname{LayerNormalization}$ denotes layer normalization applied to the vector inside
  its parentheses.  Superscript $(r)$ labels the residual block, while
  subscripts such as $a_1$ and $a_2$ label different layer normalization
  modules inside that block; they are not tensor
  coordinates.  For a vector $\vect{v}\in\R^{H_{\psi}}$, one common form is
  $\operatorname{LayerNormalization}(\vect{v})
  =
  \vect{g}\odot
  (\vect{v}-\bar{v}\mathbf{1})/\sqrt{s_v^2+\eps}
  +
  \vect{d}$,
  where $\bar{v}=H_{\psi}^{-1}\sum_{a=1}^{H_{\psi}}v^a$,
  $s_v^2=H_{\psi}^{-1}\sum_{a=1}^{H_{\psi}}(v^a-\bar{v})^2$, and
  $\vect{g},\vect{d}\in\R^{H_{\psi}}$ are learned coordinatewise scale and shift
  vectors.
} to the last hidden state as:
\[
  \vect{\psi}_{\mathrm{out}}
  =
  \operatorname{LayerNormalization}_{\mathrm{out}}
  \left(
    {}_{\psi}\vect{h}^{(R_{\psi})}
  \right)
  \in \R^{H_{\psi}}.
\]

Based on the shared backbone output $\vect{\psi}_{\mathrm{out}}$, we apply three
one-layer activationless affine readout branches: one for raw
mixture activations $\tilde{\alpha}$, one for component means $\mu$, and one
for raw scales $\beta$.%
\note{
  The parameters ${}_{\psi}\mat{W}_{(\cdot)}$ and
  ${}_{\psi}\vect{b}_{(\cdot)}$ are the weight and bias of the affine readout
  layer.  The lower-left $\psi$ marks them as MDN
  parameters.
}

After the affine outputs are formed, they are reshaped into channel, horizon,
mixture, and feature axes:

\[
  \begin{aligned}
    \tensor{\tilde{\alpha}}_{u\,v}
    &=
    {}_{\psi}\mat{W}_{\tilde{\alpha}}\cdot\vect{\psi}_{\mathrm{out}}
    +
    {}_{\psi}\vect{b}_{\tilde{\alpha}}
    \quad \in \R^{C \times H_f \times K},\\
    \tensor{\mu}_{u\,v}
    &=
    {}_{\psi}\mat{W}_{\mu}\cdot\vect{\psi}_{\mathrm{out}}
    +
    {}_{\psi}\vect{b}_{\mu}
    \quad \in \R^{C \times H_f \times K \times D_f},\\
    \tensor{\beta}_{u\,v}
    &=
    {}_{\psi}\mat{W}_{\beta}\cdot\vect{\psi}_{\mathrm{out}}
    +
    {}_{\psi}\vect{b}_{\beta}
    \quad \in \R^{C \times H_f \times K \times D_f}.
  \end{aligned}
\]

Equivalently, for every forecast channel $c=1,\ldots,C$, forecast step
$i=1,\ldots,H_f$, and mixture component $k=1,\ldots,K$.  For the future target feature vector in
$\R^{D_f}$, these outputs expose:
\[
  \tilde{\alpha}_{u\,v}^{c\,i\,k}\in\R,
  \qquad
  \vect{\mu}_{u\,v}^{c\,i\,k}\in\R^{D_f},
  \qquad
  \vect{\beta}_{u\,v}^{c\,i\,k}\in\R^{D_f}.
\]
The scalar
$\tilde{\alpha}_{u\,v}^{c\,i\,k}$ is the raw activation for mixture component
$k$; the vector $\vect{\mu}_{u\,v}^{c\,i\,k}$ is that component's
$D_f$-dimensional mean; and the vector $\vect{\beta}_{u\,v}^{c\,i\,k}$ is the
raw scale vector that will be transformed into a positive scale.

The collection index $\{c\,i\,k\}$ means that these three quantities are emitted
for every forecast channel, forecast step, and mixture component.  The lower
edge label ${u\,v}$ records that the output was computed from the edge
representation $\tensor{z}_{u\,v}$ for $e=(u,v)$.







\subsection{From Edge Forecast Network Outputs to Edge Forecast Gaussian Mixtures}
\label{subsec:from-mdn-to-mixtures}

We go from model outputs 
$\{\tensor{\tilde{\alpha}},\,\tensor{\mu},\,\tensor{\beta}\}$
to the distribution's density parameters $\{\alpha,\,\vect{\mu},\,\mat{\Sigma}\}$.

For each directed edge $e=(u,v)$, forecast channel $c$, and forecast horizon
$i$, the MDN defines a $K$-component Gaussian mixture over the selected future
target vector $\tensor{f}_{u\,v}^{c\,i}\in\R^{D_f}$.

The mixture coefficients%
\note{
  In the diagonal case used here, variances are the squared positive scales.  
  The softmax converts the raw activations $\vect{\tilde{\alpha}}_{u\,v}^{c\,i}$
  into nonnegative mixture coefficients by
  $\softmax(\vect{a})=\exp(\vect{a})/\sum_k\exp(a_k)$.  This guarantees that
  the coefficients form a simplex vector: each component is in $[0,1]$ and the
  components sum to one.
}
are
\[
  \vect{\alpha}_{u\,v}^{c\,i}
  =
  \softmax(\vect{\tilde{\alpha}}_{u\,v}^{c\,i})
  \in [0,1]^K,
  \qquad
  \sum_{k=1}^{K}\alpha_{u\,v}^{c\,i\,k}=1.
\]

The component means are slices of the reshaped mean-head output:
\[
  \vect{\mu}_{u\,v}^{c\,i\,k}
  =
  \left(
    \tensor{\mu}_{u\,v}^{c}
  \right)^{i\,k}
  \in\R^{D_f}.
\]


The raw scale vector is transformed coordinatewise into positive component
scales.  These scales define a diagonal component covariance%
\note{
  The current head emits only coordinatewise scales, so each Gaussian component
  has a diagonal covariance matrix.  This means cross-feature covariance is not
  modeled inside a single component.  The mixture as a whole may still express
  cross-feature structure through different component means and mixture
  coefficients.  A full-covariance MDN would require emitting a
  positive-definite covariance matrix for each component, commonly by predicting
  a Cholesky factor.  That richer parameterization is left as a future
  extension.
}:
\[
  \vect{\sigma}_{u\,v}^{c\,i\,k}
  =
  \softplus(\vect{\beta}_{u\,v}^{c\,i\,k})+\eps\mathbf{1}
  \in\Rpos^{D_f},
  \qquad
  \eps\in\Rpos,
\]
\[
  \mat{\Sigma}_{u\,v}^{c\,i\,k}
  =
  \diag
  \left(
    (\vect{\sigma}_{u\,v}^{c\,i\,k})^{2}
  \right)
  \in\R^{D_f\times D_f}.
\]

It follows that the predictive density for one future vector is
\[
  {}_{\psi}p_{u\,v}^{c\,i}(\tensor{f}_{u\,v}^{c\,i}\given\tensor{z}_{u\,v})
  :=
  \sum_{k=1}^{K}
  \alpha_{u\,v}^{c\,i\,k}\cdot
  \mathcal{N}
  \left(
    \tensor{f}_{u\,v}^{c\,i};
    \vect{\mu}_{u\,v}^{c\,i\,k},
    \mat{\Sigma}_{u\,v}^{c\,i\,k}
  \right)
  \in\Rnonneg.
\]

So finally, for every edge $e=(u,v)$, forecast channel $c$, and horizon $i$, the MDN
defines one Gaussian-mixture predictive distribution with density
${}_{\psi}p_{u\,v}^{c\,i}(\cdot\given\tensor{z}_{u\,v})$%
\note{
  For $\vect{f},\vect{\mu}\in\R^{D_f}$ and positive-definite
  $\mat{\Sigma}\in\R^{D_f\times D_f}$, the Gaussian density is
  $
    \mathcal{N}(\vect{f};\vect{\mu},\mat{\Sigma})
    =
    \left((2\pi)^{D_f}\det(\mat{\Sigma})\right)^{-1/2}
    \exp\!\left(
      -\frac{1}{2}
      (\vect{f}-\vect{\mu})^{\top}
      (\mat{\Sigma})^{-1}
      (\vect{f}-\vect{\mu})
    \right)
  $.
}.

\[
  {}_{\psi}\mathfrak{D}_{u\,v}^{c\,i}
  \in
  \mathcal{P}(\R^{D_f}).
\]
This is an edge-local predictive distribution%
\note{
  $\mathcal{P}(\R^{D_f})$ denotes the collection of probability distributions
  whose outcomes are vectors in $\R^{D_f}$.  In this case,
  ${}_{\psi}\mathfrak{D}_{u\,v}^{c\,i}$ is one such distribution, and
  ${}_{\psi}p_{u\,v}^{c\,i}$ is its density.
  The MDN head defines one predictive distribution for each directed edge,
  forecast channel, and forecast step.  It does not by itself define a joint
  probability distribution over all active edges, channels, or horizons.  When
  the training loss sums the NLL over $(c,i)$, it is using a pointwise
  conditional likelihood over channel-horizon targets.  Observer operators later
  decide what to read from these edge-level distributions, and the edge-to-node
  procedure decides how selected scalar edge readouts are lifted back into node
  coordinates.  A joint cross-edge, cross-channel, or cross-horizon uncertainty
  model is a separate design choice.
}.





\newpage{}
\subsection{Mixture Density Network's Training Loss}
\label{subsec:mdn-training-loss}

Fix one directed edge $e=(u,v)\in\mathcal{E}$.  In the training equations
below, the leading index $b$ denotes a sample in the homogeneous batch assigned
to this edge%
\note{
  The current edge-specialized setting trains one MDN head per directed edge.
  Therefore the batch index $b$ enumerates repeated windows for the fixed edge,
  not different edges: $e^1=\cdots=e^B=(u,v)$.
  The lower edge label $u\,v$ is kept on the batch tensors below to make this
  ownership explicit.  Mixed-edge batches would require routing by $e^b$ or a
  shared edge-conditioned forecast head.
}.
The future mask decides which target positions are allowed to contribute:
\[
  \mathcal{I}_{f,u\,v}
  =
  \left\{
    (b,c,i) : {}_{f}m_{u\,v}^{b\,c\,i}=1
  \right\}
  \subseteq
  \{1,\ldots,B\}
  \times
  \{1,\ldots,C\}
  \times
  \{1,\ldots,H_f\}.
\]
If $(b,c,i)\notin\mathcal{I}_{f,u\,v}$, the target slice is not treated as observed
training evidence%
\note{
  The future mask ${}_{f}m_{u\,v}^{b\,c\,i}$ is a supervision mask.  It should not be
  confused with the input mask used by the representation encoder.  A sample may
  have a usable input window and still have some missing future targets.
}.

The target values used by this loss are normalized future coordinates%
\note{
  The loss is computed in normalized target coordinates, not in raw market
  units.  The model assigns density to normalized future \texttt{kline}
  features, such as log-return price coordinates and \texttt{log1p} activity
  coordinates.  Any interpretation in raw market units must pass through the
  inverse normalization or through a clearly named observer.
}.

The scale used in the loss is the positive scale emitted by the head, possibly
after numerical protection.  For each batch sample and mixture component,
\[
  \vect{\sigma}_{u\,v}^{b\,c\,i\,k}\in\Rpos^{D_f},
  \qquad
  \sigma_{u\,v}^{b\,c\,i\,k\,d}
  =
  \left(\vect{\sigma}_{u\,v}^{b\,c\,i\,k}\right)^d\in\Rpos.
\]
Coordinatewise, write
\[
  \bar{\sigma}_{u\,v}^{b\,c\,i\,k\,d}
  =
  \max
  \left(
    \sigma_{\min},
    \sigma_{u\,v}^{b\,c\,i\,k\,d}
  \right)
  \in\Rpos,
  \qquad
  \sigma_{\min}\in\Rpos.
\]
An implementation may also apply an upper clamp
$\bar{\sigma}_{u\,v}^{b\,c\,i\,k\,d}\le \sigma_{\max}$ with
$\sigma_{\max}\in\Rpos$.  If no clamp is used, then
$\bar{\sigma}_{u\,v}=\sigma_{u\,v}$%
\note{
  Scale protection is part of stable training.  Very small predicted scales can
  create exploding losses and unstable gradients, while very large scales can
  make the density too diffuse.  The chosen $\sigma_{\min}$, optional
  $\sigma_{\max}$, and any gradient clipping rule should be treated as
  experiment configuration and recorded with the run.
}.

For one valid target position $(b,c,i)$ and one mixture component $k$, define
the coordinate log-density
\[
  g_{u\,v}^{b\,c\,i\,k\,d}
  :=
  \log
  \mathcal{N}
  \left(
    f_{u\,v}^{b\,c\,i\,d};
    \mu_{u\,v}^{b\,c\,i\,k\,d},
    (\bar{\sigma}_{u\,v}^{b\,c\,i\,k\,d})^{2}
  \right)
  \in\R,
\]
that is,
\[
  g_{u\,v}^{b\,c\,i\,k\,d}
  =
  -\frac{1}{2}
  \left[
    \left(
      \frac{
        f_{u\,v}^{b\,c\,i\,d}-\mu_{u\,v}^{b\,c\,i\,k\,d}
      }{
        \bar{\sigma}_{u\,v}^{b\,c\,i\,k\,d}
      }
    \right)^{2}
    +
    2\log \bar{\sigma}_{u\,v}^{b\,c\,i\,k\,d}
    +
    \log(2\pi)
  \right]
  \in\R.
\]
The diagonal Gaussian component log-density is then
\[
  q_{u\,v}^{b\,c\,i\,k}
  =
  \sum_{d=1}^{D_f} g_{u\,v}^{b\,c\,i\,k\,d}
  \in\R.
\]
The unweighted MDN negative log-likelihood is
\[
  \ell_{u\,v}^{b\,c\,i}
  =
  -
  \operatorname{logsumexp}_{k}
  \left(
    \log \alpha_{u\,v}^{b\,c\,i\,k}
    +
    q_{u\,v}^{b\,c\,i\,k}
  \right)
  \in\R.
\]
Equivalently,
\[
  \ell_{u\,v}^{b\,c\,i}
  =
  -
  \log
  \left[
    \sum_{k=1}^{K}
    \alpha_{u\,v}^{b\,c\,i\,k}
    \prod_{d=1}^{D_f}
    \mathcal{N}
    \left(
      f_{u\,v}^{b\,c\,i\,d};
      \mu_{u\,v}^{b\,c\,i\,k\,d},
      (\bar{\sigma}_{u\,v}^{b\,c\,i\,k\,d})^{2}
    \right)
  \right]
  \in\R.
\]
In code, $\log\alpha_{u\,v}^{b\,c\,i\,k}$ is usually obtained by applying
\texttt{log\_softmax} to the raw mixture activations
$\vect{\tilde{\alpha}}_{u\,v}^{b\,c\,i}$, rather than by taking the logarithm of an
already rounded softmax output%
\note{
  The implementation should compute the mixture likelihood in log space:
  \texttt{log\_softmax} for mixture weights, coordinate log-densities for the
  Gaussian factors, and \texttt{logsumexp} across mixture components.  Directly
  multiplying many small Gaussian densities is numerically fragile.
}.

The implementation may also use feature weights
${}_{d}\lambda^{(d)}\in\Rnonneg$.  In that case, replace $q_{u\,v}^{b\,c\,i\,k}$ by the
weighted score
\[
  {}_{\lambda}q_{u\,v}^{b\,c\,i\,k}
  =
  \sum_{d=1}^{D_f}
  {}_{d}\lambda^{(d)}\cdot g_{u\,v}^{b\,c\,i\,k\,d}
  \in\R,
\]
and use
\[
  {}_{\lambda}\ell_{u\,v}^{b\,c\,i}
  =
  -
  \operatorname{logsumexp}_{k}
  \left(
    \log \alpha_{u\,v}^{b\,c\,i\,k}
    +
    {}_{\lambda}q_{u\,v}^{b\,c\,i\,k}
  \right)
  \in\R.
\]
When all feature weights are equal to one,
${}_{\lambda}\ell_{u\,v}^{b\,c\,i}$ reduces to the ordinary MDN negative
log-likelihood.  When the feature weights are not all one, the expression is a
weighted training score rather than a normalized probability density; this is
acceptable as a design choice, but it should be named as such%
\note{
  Feature weights ${}_{d}\lambda^{(d)}$ change the meaning of the objective.  They
  can be useful for training emphasis, but the resulting score should not be
  reported as an exact normalized likelihood without qualification.
}.

Let ${}_{c}\lambda^{(c)}\in\Rnonneg$ be an optional channel weight and let
${}_{i}\lambda^{(i)}\in\Rnonneg$ be an optional horizon weight.  Define
\[
  {}_{f}\omega_{u\,v}^{b\,c\,i}
  =
  {}_{f}m_{u\,v}^{b\,c\,i}
  \cdot
  {}_{c}\lambda^{(c)}
  \cdot
  {}_{i}\lambda^{(i)}
  \in\Rnonneg.
\]
The channel and horizon weights express training emphasis%
\note{
  Channel weights ${}_{c}\lambda^{(c)}$ and horizon weights ${}_{i}\lambda^{(i)}$
  decide which resolutions and forecast positions receive more learning
  pressure.  They should be chosen deliberately, not left as hidden constants in
  the training loop.
}.
The masked batch loss is
\[
  \mathcal{L}_{\mathrm{MDN},u\,v}
  =
  \frac{
    \sum_{b=1}^{B}
    \sum_{c=1}^{C}
    \sum_{i=1}^{H_f}
    {}_{f}\omega_{u\,v}^{b\,c\,i}\cdot
    {}_{\lambda}\ell_{u\,v}^{b\,c\,i}
  }{
    \sum_{b=1}^{B}
    \sum_{c=1}^{C}
    \sum_{i=1}^{H_f}
    {}_{f}\omega_{u\,v}^{b\,c\,i}
  }
  \in\R.
\]
Only valid future positions contribute.  If the denominator is zero, the batch
does not contain supervised evidence for this head and should be skipped or
handled by the training loop's numerical guard%
\note{
  Silently forcing the masked denominator to a small constant can hide dataloader
  or masking problems.  A zero-denominator batch should be treated as an explicit
  no-evidence case.
}.

This loss trains the whole predictive distribution.  It does not ask the head
to make only the mixture mean accurate; it rewards the model for placing high
density on the observed future target, including the scale and mixture-weight
choices that express uncertainty%
\note{
  Mean-squared error of the expectation may be monitored as a diagnostic, but it
  is not the training objective unless a separate observer-level loss is added.
}.
The MDN loss is pointwise over channel-horizon target slices%
\note{
  Summing over $(c,i)$ does not, by itself, define a joint probability distribution over
  all channels and all horizons.  Any trajectory score, cumulative-return score,
  or cross-horizon uncertainty model is a later readout assumption unless a
  joint head is explicitly introduced.
}.
During validation, the useful diagnostics include held-out negative
log-likelihood, finite-value checks, scale statistics, mixture-weight entropy,
component usage, observer errors for means and quantiles, and coverage of
predictive intervals%
\note{
  These checks help detect mixture collapse, overconfident scales, unused
  components, bad masks, or distributional miscalibration before the readouts are
  used by downstream graph recovery.
}.



\newpage{}
\subsection{Expectation and covariance readouts}
\label{subsec:mdn-expectation-and-covariance}

After training, the MDN distribution can be read in several ways.  The first
readout is the expected future vector, available in closed form:
\[
  \widehat{\tensor{f}}_{u\,v}^{c\,i}
  =
  {}_{\psi}\E
  \left[
    \tensor{f}_{u\,v}^{c\,i}\given\tensor{z}_{u\,v}
  \right]
  =
  \sum_{k=1}^{K}
  \alpha_{u\,v}^{c\,i\,k}\cdot
  \vect{\mu}_{u\,v}^{c\,i\,k}
  \in\R^{D_f}.
\]
In batch form,
\[
  \widehat{\tensor{f}}
  \in
  \R^{B\times C\times H_f\times D_f}.
\]

The full covariance of the mixture distribution is also closed form.  Let
\[
  \mat{C}_{u\,v}^{c\,i}
  :=
  {}_{\psi}\Cov
  \left[
    \tensor{f}_{u\,v}^{c\,i}
    \given
    \tensor{z}_{u\,v}
  \right]
  \in\R^{D_f\times D_f}.
\]
Then the expresion for the full covariance readout becomes,
\[
  \mat{C}_{u\,v}^{c\,i}
  =
  \sum_{k=1}^{K}
  \alpha_{u\,v}^{c\,i\,k}\cdot
  \left(
    \mat{\Sigma}_{u\,v}^{c\,i\,k}
    +
    \vect{\mu}_{u\,v}^{c\,i\,k}
    (\vect{\mu}_{u\,v}^{c\,i\,k})^{\top}
  \right)
  -
  \widehat{\tensor{f}}_{u\,v}^{c\,i}
  (\widehat{\tensor{f}}_{u\,v}^{c\,i})^{\top}
  \in\R^{D_f\times D_f}.
\]
The products with transposed vectors are outer products%
\note{
  For $\vect{a}\in\R^{D_f}$, the expression
  $\vect{a}(\vect{a})^{\top}$ is a $D_f\times D_f$ outer product, not a
  scalar dot product.
}. Although each component covariance $\mat{\Sigma}_{u\,v}^{c\,i\,k}$ is diagonal,
this mixture covariance can contain off-diagonal terms through the component
means.  This is one reason the mixture should be treated as a distribution over
the full target vector, not only as a list of independent scalar forecasts.




\subsection{Scalar edge-return marginal}
\label{subsec:mdn-scalar-edge-return-marginal}

\calloutbox{}{%
  Some downstream graph operations use one scalar return coordinate rather than
  the full future vector. They requires a scalar edge quantity whose
  meaning is a relative value change between two nodes, usually the \texttt{close returns} coordinate.
}

Let $(r)$ denote the selected scalar return coordinate
inside the future target vector.

The scalar predictive density is the marginal mixture
\[
  {}_{\psi}p_{(r),u\,v}^{c\,i}(f_{u\,v}^{c\,i\,(r)}\given\tensor{z}_{u\,v})
  =
  \sum_{k=1}^{K}
  \alpha_{u\,v}^{c\,i\,k}\cdot
  \mathcal{N}
  \left(
    f_{u\,v}^{c\,i\,(r)};
    \mu_{u\,v}^{c\,i\,k\,(r)},
    (\sigma_{u\,v}^{c\,i\,k\,(r)})^{2}
  \right)
  \in\Rnonneg.
\]
and the corresponding scalar predictive distribution is
\[
  {}_{\psi}\mathfrak{D}_{(r),u\,v}^{c\,i}
  \in\mathcal{P}(\R),
  \qquad
  \text{with density }
  {}_{\psi}p_{(r),u\,v}^{c\,i}(\cdot\given\tensor{z}_{u\,v}).
\]
Its expectation is
\[
  \widehat{r}_{u\,v}^{c\,i}
  =
  \sum_{k=1}^{K}
  \alpha_{u\,v}^{c\,i\,k}\cdot
  \mu_{u\,v}^{c\,i\,k\,(r)}
  \in\R,
\]
and $(r)-th$ marginal variance is
\[
  {}_{\psi}\Var
  \left[
    f_{u\,v}^{c\,i\,(r)}
    \given
    \tensor{z}_{u\,v}
  \right]
  =
  \sum_{k=1}^{K}
  \alpha_{u\,v}^{c\,i\,k}\cdot
  \left(
    (\sigma_{u\,v}^{c\,i\,k\,(r)})^{2}
    +
    (\mu_{u\,v}^{c\,i\,k\,(r)})^{2}
  \right)
  -
  (\widehat{r}_{u\,v}^{c\,i})^{2}
  \in\Rnonneg.
\]
These scalar distributions are the objects read by the edge observers in
Section~\ref{sec:distribution-field-and-observer-operators} and by the
edge-to-node recovery step in Section~\ref{sec:edges-to-nodes}.
