\section{Normalization Procedure}
\label{app:normalization}

This appendix records the current normalization pass used by the dataloader
when the cache is built with the \field{log\_returns} policy.  The pass is
causal and channel-local: each valid candle is normalized using only the
previous valid candle on the same channel.

\subsection{Causal Scan on One Channel}
\label{appsub:causal-scan-on-one-channel}

Normalization is applied after the CSV has already been sanitized onto a
regular key lattice.  The raw cache and the normalized cache therefore have the
same record count and the same key values.  The pass scans the channel from
left to right while maintaining one state variable: the previous valid candle
on that same channel.

For each record, the implementation does the following:
\begin{enumerate}
\item If the current record is invalid, it is written through unchanged and the
previous-valid state is cleared.
\item If the current record is valid but there is no previous valid candle, the
current record is replaced by a null instance at the same key value.
\item If both the current record and the previous valid candle are available,
the current record is normalized in place.
\end{enumerate}

As a consequence, the first valid candle of every contiguous valid segment is
masked out, because there is no causal reference close available for it.

\subsection{Per-Field Transform}
\label{appsub:per-field-transform}

For one valid candle, write the price tuple as
\[
  (p^{\mathrm{open}}, p^{\mathrm{high}}, p^{\mathrm{low}}, p^{\mathrm{close}})
  \in \Rpos^{4},
\]
and the activity tuple as
\[
  (a^{\mathrm{volume}}, a^{\mathrm{quote}}, a^{\mathrm{trades}},
   a^{\mathrm{buybase}}, a^{\mathrm{buyquote}})
  \in \Rnonneg^{5}.
\]
Let $\mathrm{cp}(t-1) \in \Rpos$ be the \field{close\_price} of the previous
valid candle on the same channel.  The four price coordinates are then mapped
as
\[
  \log\!\bigl(p^{\mathrm{open}}/\mathrm{cp}(t-1)\bigr), \qquad
  \log\!\bigl(p^{\mathrm{high}}/\mathrm{cp}(t-1)\bigr), \qquad
  \log\!\bigl(p^{\mathrm{low}}/\mathrm{cp}(t-1)\bigr), \qquad
  \log\!\bigl(p^{\mathrm{close}}/\mathrm{cp}(t-1)\bigr).
\]
The five non-price coordinates are mapped coordinatewise by
\[
  \begin{aligned}
    &\log(1+a^{\mathrm{volume}}), \qquad
    \log(1+a^{\mathrm{quote}}), \qquad
    \log(1+a^{\mathrm{trades}}), \\
    &\log(1+a^{\mathrm{buybase}}), \qquad
    \log(1+a^{\mathrm{buyquote}}).
  \end{aligned}
\]

For kline records, this produces the 9-dimensional normalized feature vector
used in the main text:
\[
  \tensor{x}_{u\,v}^{b\,c\,i}(t) \in \R^{D_x},
  \qquad D_x = 9.
\]

\subsection{Domain Protection}
\label{appsub:domain-protection}

The implementation keeps the normalization numerically finite even when the raw
record is malformed.  For price-return coordinates, any nonpositive or
non-finite price input is clamped to the positive floor $10^{-12}$ before the
logarithm is applied; the same floor is used if the reference
\field{close\_price} is nonpositive or non-finite.

For the activity coordinates, any value less than or equal to $-1$, or any
non-finite value, is clamped to $-1 + 10^{-12}$ before applying
$\log(1+\cdot)$.  The normalizer emits warning summaries for these events, but
the resulting cache remains finite and keeps the same lattice structure.
